Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
off by 1 and 2 errors

\begin{definition}[Use return seals only for call]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, then either $\src{\Phi'}$ is inside $\src{\scall{o}{r_1'}{r_2'}}$ and $\sigma_\baddr \leq \sigma \leq \sigma_\baddr + \nrcalls$ or $\sigma_\baddr + \nrcalls < \sigma \leq \sigma_\baddr + \nrcalls + \nrclosures+1$.
\end{definition}

>>>>

\begin{definition}[Use return seals only for call]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, then either $\src{\Phi'}$ is inside $\src{\scall{o}{r_1'}{r_2'}}$ and $\sigma_\baddr \leq \sigma < \sigma_\baddr + \nrcalls$ or $\sigma_\baddr + \nrcalls \leq \sigma < \sigma_\baddr + \nrcalls + \nrclosures$.
\end{definition}
